Bayesian integration of networks without gold standards

### 2011-08-20 src/main/latex/paper/paper.tex
extending results section

The next step consists of the simulation of experimental measurements on the true graph. This is the most crucial step of the artificial testing environment as it is responsible for replicating all the different faults and problems of real data. The simplest type of error occurring in experimental measurements is random noise. This type of error is easily simulated by randomly inserting edges that do not exist in the real data and removing edges that do exist in the real data until the desired error rates are reached. The next problem is systematic error or experimental bias. This phenomenon in particular leads to the violation of stochastic independence between datasets. 
\note{TODO: Bias simulation has yet to be implemented.}%TODO <-- 
Finally, another type of error that easily escapes one's attention is the lack of negative records. Most experiments do not report which pairs of nodes do not possess an edge. As a consequence, it is hard to differentiate between node pairs that have been observed not to interact and node pairs that have not been subject to testing. 
\note{TODO: Low-throughput experiments have yet to be implemented}%TODO <--

@@

\begin{align} 
	L^{(+)} &= \frac{1}{|E_G|}\sum_{e \in E_G} (1 - \prob(e \in E_G|X))^2\\
	L^{(-)} &= \frac{1}{|\binom{V}{2} \setminus E_G|}\sum_{e \in \binom{V}{2} \setminus E_G} \prob(e \in E_G|X)^2
\end{align}.
Other performance metrics such as the area under ROC curves or weighted sums over the quadratic loss functions above are also possible to apply. However we find that the separate loss functions shown above give a more detailed picture of a method's behaviour.
\note{Maybe move to discussion. Discuss other possible scoring functions, e.g. weighted sums over FPs and FNs}

@@

Figure \ref{htp} shows the methods' performances over different numbers of input HTP experiments. It is clearly visible that the new fully Bayesian method outperforms both gold standard-based methods, particularly given a low number of input datasets.

@@

When given a mixed set of HTP and LTP experiments, ...\note{TODO: Implement LTP simulation}

@@

>>>>

The next step consists of the simulation of experimental measurements on the true graph. This is the most crucial step of the artificial testing environment as it is responsible for replicating all the different faults and problems of real data. The simplest type of error occurring in experimental measurements is random noise. This type of error is easily simulated by randomly inserting edges that do not exist in the real data and removing edges that do exist in the real data until the desired error rates are reached. The next problem is systematic error or experimental bias. This phenomenon in particular leads to the violation of stochastic independence between datasets. 
\note{TODO: Bias simulation has yet to be implemented.}%TODO <-- 
Finally, another type of error that easily escapes one's attention is the lack of negative records. Most experiments do not report which pairs of nodes do not possess an edge. As a consequence, it is hard to differentiate between node pairs that have been observed not to interact and node pairs that have not been subject to testing.

@@

\begin{align} 
	L^{(+)} &= \frac{1}{|E_G|}\sum_{e \in E_G} (1 - \prob(e \in E_G|X))^2\\
	L^{(-)} &= \frac{1}{|\binom{V}{2} \setminus E_G|}\sum_{e \in \binom{V}{2} \setminus E_G} \prob(e \in E_G|X)^2
\end{align}.

@@

Figure \ref{htp} shows the methods' performances over different numbers of input HTP experiments. It is clearly visible that the new fully Bayesian method overall outperforms both gold standard-based methods. For low numbers of input datasets, the loss over existing interactions is significantly lower. Given more than five HTP experiments, all methods show comparably low loss of existing interactions.

Regarding non-existing interactions the fully Bayesian method constantly performs better than the method presented by James and colleagues. \note{See if we can get rid of Lee's strange behaviour here, by using a different threshold.}

The average loss regarding the $\theta$ estimates shows the fully Bayesian method's superior precision, which increases with the number of input experiments, while both gold standard-based methods stagnate at constant large amout of loss.

\note{TODO: re-run on biased data}

\note{TODO: Show some stats on the integration of real data}

@@

%When given a mixed set of HTP and LTP experiments, ...\note{TODO: Implement LTP simulation}

@@

%In addition to the performance metrics used here, others such as the area under ROC curves or weighted sums over the quadratic loss functions above are also possible to apply. However we find that the separate loss functions shown above give a more detailed picture of a method's behaviour.
%\note{Discuss other possible scoring functions, e.g. weighted sums over FPs and FNs}
